Using the internal language of toposes in algebraic geometry

### 2014-06-20 poster.tex
typo

    \begin{center}
      \begin{tabular}{ll}
        \toprule
        external point of view & internal point of view \\
        \midrule
        objects of~$\E$ & sets \\
        morphisms of~$\E$ & maps of sets \\
        monomorphisms in~$\E$ & surjective maps \\
        epimorphisms in~$\E$ & injective maps \\
        \bottomrule
      \end{tabular}
    \end{center}
  \end{block}

>>>>

    \begin{center}
      \begin{tabular}{ll}
        \toprule
        external point of view & internal point of view \\
        \midrule
        objects of~$\E$ & sets \\
        morphisms of~$\E$ & maps of sets \\
        monomorphisms in~$\E$ & injective maps \\
        epimorphisms in~$\E$ & surjective maps \\
        \bottomrule
      \end{tabular}
    \end{center}
  \end{block}
